---
title: "Tutorial of \"MODIS\" Package"
author: "Michael Li"
date: "2021/10/21"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initialization: MODISoptions()

```{r}
#devtools::install_github("https://github.com/MatMatt/MODIS")
library(MODIS)
```
First of all, we need to library the "MODIS" package. If that is uninstalled, then run the first sentence.

Guarantee you know every thing about the Products you are going to use, such as PixelSize, outproj, resamplingType <https://gdal.org/programs/gdalwarp.html>. Since we prefer to to use WGS 84 proj, the outproj could be set "EPSG:4326".

```{r}
?MODISoptions()
MODISoptions(localArcPath = "D:\\09_Article\\X0_test",
             outDirPath = "D:\\09_Article\\X0_test\\PROCESSED",
             resamplingType = "average", outProj = "EPSG:4326",
             pixelSize = 0.25)
```

Before that, you need to know SDSstring. So, run getSds(). For example:
```{r}
getSds(HdfName = "D:\\09_Article\\05_Moisture\\MOD07_2009\\MOD07_L2.A2009001.0130.061.2017296025029.hdf")
```
If we only want to get the Cloud_Mask only, there would only 8th digit 1. "0000000100000000000000000000"  
However, here we still do not know the information about the product. Therefore, we run getProduct():
```{r}
getProduct(x = "MOD11A2")
```


Now, let us try!
```{r}
runGdal(product="MOD11A2", extent="austria", begin="2010001", end="2010020", SDSstring="100", overwrite = T)
```
Note